Quality Definitions of Qualities

### 2021-10-08 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
added definition of unambiguity, chose definition, added reasoning

\begin{mybox}
\subsubsection*{Unambiguity} 
\wss{Needs to be completed.}
\end{mybox}

@@

>>>>

\begin{defn}
	\label{UnambiguitySelected} (1) Not having two or more possible meanings. (2) Not susceptible to different interpretations. (3) Not obscure, not vague. (4) Clear, definite, certain. \citep{FDA2014}.
\end{defn}

\begin{mybox}
\subsubsection*{Unambiguity} 
Definition~\ref{UnambiguitySelected} rephrased: Unambiguity is the quality of having one clear interpretation, and not having any other possible interpretations.
\end{mybox}

@@

\begin{itemize}
  \item This definition succinctly encompasses parts of the chosen definition, and includes the basis of the alternate definition.
\end{itemize}
